Classless Java

### 2016-03-23 OOPSLA16/sections/Appendix_Formalization.tex
Appendices A and B commented.

\section{Expanded related work}\label{sec:ERW}

@@

@@

This section presents a formalization of Classless Java, \delete{a minimal
FeatherweightJava-like calculus} which models the essence of Java
interfaces with default methods. This formalization is used \delete{in
Section~\ref{sec:translation}} to define the semantics of object interfaces.

>>>>

%% Appendices A & B commented
\begin{comment}
\section{Expanded related work}\label{sec:ERW}

@@

\end{comment}

@@

This section presents a formalization of Classless Java, which models the essence of Java
interfaces with default methods. This formalization is used to define the semantics of object interfaces.
